---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
<br>

# demsrc

<!-- badges: start -->
[![R-CMD-check](https://github.com/Permian-Global-Research/demsrc/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Permian-Global-Research/demsrc/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Permian-Global-Research/demsrc/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Permian-Global-Research/demsrc?branch=main)
<!-- badges: end -->

The goal of demsrc is to return the remote url sources for global DEM products.
For now, the only main function is `mpc_dtm_src` which accesses the collections
via the [Microsoft Planetary Computer STAC catalog](https://planetarycomputer.microsoft.com/catalog) 
using the [{rstac} package](https://brazil-data-cube.github.io/rstac/)

## Installation

You can install the development version of demsrc from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Permian-Global-Research/demsrc")
```

## Example

Here we load a few packages...

```{r pkg-load, message=FALSE, warning=FALSE}
library(demsrc)
library(terra)
library(sf)
```

And now we request the ALOS DEM urls for the Mount Hood area in Oregon using 
the bounding box coordinates.
```{r Mt-Hood-example}
(mh <- mpc_dtm_src(c(-121.772, 45.321, -121.611, 45.419),
  collection = "alos-dem"
))

plot(rast(mh))
```

And now to get the COP30 DEM urls for the North Carolina dataset, using and 
sf object as the area of interest.

```{r nc-example}
nc_sf <- system.file("gpkg", "nc.gpkg", package = "sf") |>
  read_sf()

# show the first 3 urls:
mpc_dtm_src(nc_sf, collection = "cop-dem-glo-30")[1:3]
```

